---
title: "Reproducible Research: Peer Assessment 1"
author: "Delphine"
date: "14/07/2023"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
First, we unzip data in order to obtain a csv file that we can work on and we save it into a dataframe named activity

```{r}
library("data.table")
library(ggplot2)

fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = paste0(getwd(), '/repdata%2Fdata%2Factivity.zip'), method = "curl")
unzip("repdata%2Fdata%2Factivity.zip",exdir = "data")

as.data.table(read.csv(file = "data/activity.csv", header = TRUE))
```

## What is mean total number of steps taken per day?
1. Calculate the total number of steps taken per day

```{r}
Total_Week_Steps <- activity[, c(lapply(.SD, sum, na.rm = FALSE)), .SDcols = c("steps"), by = .(date)] 

```

2.If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day

```{r}
ggplot(Total_Week_Steps, aes(x = steps)) +
    geom_histogram(fill = "blue", binwidth = 1000) +
    labs(title = "Daily Steps", x = "Steps", y = "Frequency")
```

3.Calculate and report the mean and median of the total number of steps taken per day
```{r}
Total_Week_Steps[, .(Mean_Steps = mean(steps, na.rm = TRUE), Median_Steps = median(steps, na.rm = TRUE))]
```

## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
